%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

  \cventry
    {Software Engineer} % Job title
    {Workrise} % Organization
    {Austin, Texas} % Location
    {Sep. 2021 - Nov. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and optimized RESTful APIs and event-driven microservices managing 20,000 daily requests.
        Implemented authentication,rate-limiting, and Prometheus monitoring tools, reducing errors by 40\%.}
        \item {Automated the creation of 8,000+ monthly work invites by building a Kotlin-based microservice,
          eliminating manual invite creation and saving 200+ administrative hours monthly.}
        \item {Continuously improved the infrastructure architecture since launching the service.}
        \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategy
        for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
        \item {Introduced Okta employee identity solution in the company, establishing security policies
        and configuring SSO integration with over 20 enterprise systems including GCP, GitHub, Slack, Google Workspace.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Software Engineer} % Job title
    {ExxonMobil} % Organization
    {Houston, Texas} % Location
    {Sep. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance
        and acquire a business license for financial services in Korea.}
        \item {Established a standardized base for declarative management of infrastructures and service deployments,
          enabling operational efficiency and consistency.}
        \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for
        RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
        \item {Introduced Okta employee identity solution in the company, establishing security policies
        and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Software Engineer Intern} % Job title
    {ExxonMobil} % Organization
    {Houston, Texas} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed on-boarding process to guide new engineers, help them to focus on the right tasks,
          and set expectations to help them be successful at Infrastructure team.}
        \item {Migrated the orchestration system from DC/OS to Kubernetes which is based on AWS EKS.
        Managed 3 Kubernetes clusters and 300+ pods.
        Managed all Kubernetes manifests declaratively with Kustomize and ArgoCD.}
        \item {Designed and managed complex network configurations on AWS with 4 VPC and 100+ subnets.
        Separated the development network and operation network according to financial regulations.
        Established dedicated network connections from AWS VPC to partners' on-premise network based on
        AWS Direct Connect with secure connection using IPsec VPN.
        Provisioned OpenVPN servers with LDAP integration.}
        \item {Provisioned an observability system with Kafka, Elastic, Stack(Filebeat, Heartbeat, APM Server, Logstash, Elasticsearch, Kibana).
        Collected log, uptime, tracing data from hosts, containers, pods and more.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}